Get topographic info of gps points

### 2017-03-01 analysis/analysis_competence.Rmd
updating

```{r, warning=FALSE, message=FALSE}}
#library("tidyverse")
library("dplyr")
library("ggplot2")
```

@@

compete <- read.csv(file=paste0(di, '/data/tree_compete.csv'), header=TRUE, sep=',')
```

```{r}
# prepare data

get.coords <- function(a, d, x0, y0) {
a <- ifelse(a <= 90, 90 - a, 450 - a)
data.frame(x = x0 + d * cos(a / 180 * pi),
y = y0+ d * sin(a / 180 * pi))
}

compete <- compete %>% 
  mutate(xcord = get.coords(a=rumbo_degree, 
                           d=distance_cm/100,
                           x0 = 0, y0 = 0)$x,
         ycord = get.coords(a=rumbo_degree, 
                           d=distance_cm/100,
                           x0 = 0, y0 = 0)$y)

mis <- get.coords(a=compete$rumbo_degree, 
                  d=compete$distance_cm, 
                  x0 = 0, y0 = 0)

@@

>>>>

```{r, warning=FALSE, message=FALSE}}
library("tidyverse")
```

@@

# density data 
compete <- read.csv(file=paste0(di, '/data/tree_compete.csv'), header=TRUE, sep=',')
```

```{r}
radius_plot <- 10 #
sf_plot <- pi * radius_plot^2

den_tree <- compete %>% 
  group_by(id_core) %>% 
  summarise(abun = n(), 
            den = abun*10000 / sf_plot ) # stand density (tree / ha)

diameter = perimeter/pi

ba <- compete %>% 
  mutate(dn = (diam_mm/1000) / pi, 
         dn2 = dn * dn) %>% 
  group_by(id_core) %>% 
  summarise(
    ba = (pi/4) * sum(dn2),
    ba_mean = ba / n())

get_coords_trees <- function(angle, distance, x0, y0) {
  angle <- ifelse(angle <= 90, 90 - angle, 450 - angle)
  data.frame(x = x0 + distance * cos(angle / 180 * pi),
             y = y0+ distance * sin(angle / 180 * pi))
}

compete <- compete %>% 
  mutate(xcord = get_coords_trees(angle= rumbo_degree, 
                           distance = distance_cm/100,
                           x0 = 0, y0 = 0)$x,

         ycord = get_coords_trees(angle = rumbo_degree, 
                           distance = distance_cm/100,
                           x0 = 0, y0 = 0)$y)

@@

radi <- 10 
(pi*radi*radi)/10000

```{r}

den <- compete %>% group_by(id_core) %>% 
  summarise(ntree = n(),
            den = ntree*10000 / (pi*100))

### 2017-03-01 analysis/get_elevation_points.Rmd
updating

```{r packages, warning=FALSE, message=FALSE}}
library("rgdal")
library("sp")
library("raster")
library("dplyr")
```

# Read data 
```{r wd, echo=FALSE}
# machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

# read DEM 
demsn <- raster("mde_sn_area_influencia.asc")

@@

## Projection 
# Get projection
projection(demsn)

# Set projection
crs(demsn) <- "+proj=utm +zone=30 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"

# Read points data 
gps_point <- readOGR(paste0(di, 'data_raw/geoinfo/'), layer = 'dendro_garmin', verbose = FALSE)

## reproject 
gps_point_re <- spTransform(gps_point, crs(demsn))

gps_elev <- extract(demsn, gps_point_re, method='simple', sp=TRUE)

elev <- gps_elev@data %>% 
  dplyr::select(lat, lon, elev, name, date, elev_mde = mde_sn_area_influencia)

>>>>

```{r packages, warning=FALSE, message=FALSE}}
library("rgdal")
library("sp")
library("raster")
library("dplyr")
library("maptools")
```

# Read data 
```{r wd, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

# read DEM 
# demsn <- raster("mde_sn_area_influencia.asc")
# dme5t ign 
dem1027 <- raster("1027.asc")
dem1042 <- raster("1042.asc")

@@

## Projection 
# Set projection(demsn)
crs(demsn) <- "+init=epsg:23030"

# Read points data 
gps_point_ca <- readOGR(paste0(di, 'data_raw/geoinfo/dendro_ca.GPX'), layer='waypoints', verbose = FALSE) 
gps_point_sj <- readOGR(paste0(di, 'data_raw/geoinfo/dendro_sj.GPX'), layer='waypoints', verbose = FALSE)

# Join point 
gps_point <- spRbind(gps_point_ca,gps_point_sj)

# Get elev 
gps_elev <- extract(demsn, gps_point, method='simple', sp=TRUE)

elev <- gps_elev@data %>%
  dplyr::select(ele, name, elev_mde = mde_sn_area_influencia)
